---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Marq Schieber"
date: "3/22/22"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(stringr)
library(skimr)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

### Exercise 10

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, date)
```

There were 3 warnings:
1)Discarded pieces
2)Discarded pieces replaced with NA
3)Numeric-String computation error

### Exercise 11 Print out a summary of the dataframe using the skim() function. How many pieces have artist info missing? How many have year info missing?

```{r}
skim(uoe_art)
```
artist missing = 113
year missing  1364

### Exercise 12 Make a histogram of years. Use a reasonable binwidth. Do you see anything out of the ordinary?

```{r}
ggplot(uoe_art,aes(x=year))+
geom_histogram()
```

An art piece from year 0?....

```{r}
ggplot(uoe_art,aes(x=year))+
geom_histogram()+
  coord_cartesian(xlim = c(1500 , 2022))
```

### Exercise 13 Find which piece has the out of the ordinary year and go to its page on the art collection website to find the correct year for it. Can you tell why our code didn’t capture the correct year information? Correct the error in the data frame and visualize the data again.

Death Mask. R got confused by the (2), which I'm guessing signifies it's the 2nd piece titled Death Mask.


```{r}
uoe_art_v2 <- uoe_art %>% 
  mutate(
    year = if_else(
      year == "2" , "1964" ,
      if_else(year != "2" , paste0(year), "NA"
    ))) %>% 
  mutate(year = as.numeric(year))
  
```

```{r}
ggplot(uoe_art_v2,aes(x=year))+
geom_histogram()+
  coord_cartesian(xlim = c(1500 , 2022))
```

###Who is the most commonly featured artist in the collection? Do you know them? Any guess as to why the university has so many pieces from them?

Emma Gillies. I am not familiar with her work. I'm guessing alumna? Or local artist?

```{r}
uoe_art_v2 %>% 
  count(artist) %>% 
  arrange(desc(n))
```

###Final question! How many art pieces have the word “child” in their title? See if you can figure it out, and ask for help if not.

10, tried with "child" and no results

```{r}
uoe_art_v2 %>% 
  filter(str_detect(title , "Child"))
```

